AA Distributed Software Development Methodology

### 2013-06-02 paper.tex
integrado ate linha 83 com hybrid

One of the defining features of modern times is the widening geographical
distribution of software teams~\cite{last2003} creating what is called Global
Software Development (GSD)~\cite{german2003,Fryer,Begel}.  
An example is the free software movement. Projects and institutions like Mozilla
Foundation has several employees and thousands of voluntary developers
distributed across many countries. The same is true for GNOME~\cite{german2003},
OpenBSD, MySQL or Apache Software Foundation, to cite just a 
few of the most active projects.\footnote{Ohloh, the open source network, has a more complete
and constantly updated list of the most active projects on-line at
\url{www.ohloh.net}} Along the free and open software projects, GSD is growing
popularity in every niche of the software industry as a whole, even on those
distributing their software with proprietary licenses. This phenomenon is
attributed to a variety of factors such as a larger labor pool, natural
globalization of software companies and foundations or even the premise of
cheaper cost of production~\cite{komi2005}.

Despite the advantages of GCD, we have noticed how
difficult it is to coordinate and fund free software on a larger scale
than currently available, when teams are very heterogeneous containing
not only volunteers and very experienced developers, but also
contractors and freelancers from different backgrounds and cultures. Our observations
are founded on the factors suggested by Carmel~\cite{carmel1999} as
main difficulties for GCD: distance, time and cultural differences. In
the case of free or open software projects, all these factors are
involved.

Another problem faced by modern software companies and other
collectives are frequent ineffective meetings, which are seldom
focused to the interest to any attendant. The result is that it has
become the norm to participate in too many meetings with the ``laptop
open'', which can be un-productive. Software developers
like to code, to be productive, to have their hands on their project,
to do what they are best at. They dislike to forcibly stop for meetings
or to do other bureaucratic activities such as writing lengthy reports to
justify their funding.\cite{Thompson:Wired:2012}
%\todo{ler mais. cacm, etc}

>>>>

One of the defining features of modern times is the widening geographical
distribution of software teams~\cite{last2003} creating what is called Global
Software Development (GSD)~\cite{german2003,Fryer,Begel}.  
An example is the free software movement. Projects and institutions like Mozilla
Foundation has several employees and thousands of voluntary developers
distributed across many countries. The same is true for GNOME~\cite{german2003},
OpenBSD, MySQL or Apache Software Foundation, to cite just a 
few of the most active projects.\footnote{Ohloh, the open source network, has a more complete
and constantly updated list of the most active projects on-line at
\url{www.ohloh.net}} Beyond the free and open software community, GSD has a growing
popularity in every niche of the software industry as a whole, even among those
distributing their software with proprietary licenses. This phenomenon is
attributed to a variety of factors such as a larger labor pool, natural
globalization of software companies and foundations or even the premise of
cheaper cost of production~\cite{komi2005}.

Despite the advantages of GSD, we have noticed how
difficult it is to coordinate and fund free software on a significantly larger scale
than currently practiced, as series of qualitatively new situations arise. Distributed
teams are very heterogeneous containing not only volunteers and very experienced
developers, but also contractors and freelancers from different backgrounds and
cultures. Our observations are founded on the factors suggested by
Carmel~\cite{carmel1999} as main difficulties for GSD: distance, time and
cultural differences. In the case of free or open software projects, all these
factors are involved.

Another problem faced by modern software companies and other
collectives are frequent ineffective meetings, which are seldom
focused on the particular interest of any attendant. The result is that it has
become the norm to participate in too many meetings with the ``laptop
open'', which can be un-productive. Software developers
like to code, to be productive, to have their hands on their project,
to do what they are best at. They dislike to forcibly stop for meetings
or to do other bureaucratic activities such as writing lengthy reports to
justify their funding.\cite{Thompson:Wired:2012}
%\todo{ler mais. cacm, etc}
